Technical Report

### 2024-02-19 Reports/tech_report1.tex
update tests

@@

>>>>

\subsection{Seek the best open ReLU number for layer 35 for normal 5x100}

@@

\begin{itemize}
	\item \emph{Log:} \verb*|Gamma_5x100_normal_layer5_seek_openrelu.txt|

	\item \emph{Total time:} 61891s.

	\item \emph{Key results:} $\gamma$ for different open number are 0.9664584160601942,
	0.9480190853777704,
	0.969433533659244,
	0.9832281749149849,
	0.9884851087698833. This means open 20 is the best among 5 choices.

	\item \emph{Binary data}: \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_17_21_56_00.b| and \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_17_21_56_00.b|. The first stores the gamma up to layer 3, and the second stores tests result of layer 5 in addition.
\end{itemize}

\section{February 17-18 experiments}

\subsection{Seek the best open ReLU number for layer 7 for normal 5x100}

This experiment is to find the best open ReLU number for layer 7 normal 5x100 with new hyperplane constraints.

The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number.py| (a copy for it is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number_layer7.py|). And the partial output file name is \verb*|Gamma_5x100_normal_layer7_seek_openrelu.txt|.  It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 5 with different open ReLU numbers.

\begin{itemize}
	\item\emph{Experiments Id}: 021700202024

	\item\emph{Open $\ReLU$ number:} Open 20, 24, 28, 32, 36 ReLU nodes for each node.

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b|; this file stores all alpha beta gamma of nodes of all layers for the same network (gamma is up to layer 3 and is newly-computed). 
\end{itemize}

\begin{itemize}
	\item \emph{Log:} \verb*|Gamma_5x100_normal_layer7_seek_openrelu.txt|

	\item \emph{Total time:} 40866s.

	\item \emph{Key results:} $\gamma$ for different open number are 3.924847266202133,
	3.879966384915862,
	3.843735078541843,
	3.834229593178003,
	3.816831654178999. This means open 36 is the best among 5 choices.

	\item \emph{Binary data}: \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_18_22_11_50.b| and \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_18_22_11_50.b|. The first stores the gamma up to layer 5, and the second stores tests result of layer 7 in addition.
\end{itemize}
